\LARGE \bf Mean Estimation from One-Bit Measurements

### 2022-05-09 ak-bio.tex
arranged appendix in two-columns
update bio

Alon Kipnis is a Senior Lecturer (Assistant Professor) at the School of Computer Science at Reichman University. Previously, he was a postdoctoral research scholar at the Department of Statistics at Stanford University, advised by David Donoho. He completed his Ph.D. in electrical engineering from Stanford University in 2017. His research is in the areas of mathematical statistics and information theory. He is particularly interested in ambitious machine learning and data science applications of his theoretical work.

Dr. Kipnis is the recipient of numerous fellowships and awards, including the Koret foundation postdoctoral fellowship, Stanford's electrical engineering department fellowship, and a prize from the Wolf Foundation. His research is in the areas of mathematical statistics and information theory.

>>>>

is a Senior Lecturer (Assistant Professor) at the School of Computer Science at Reichman University. Previously, he was a postdoctoral research scholar at the Department of Statistics at Stanford University, advised by David Donoho. He completed his Ph.D. in electrical engineering from Stanford University in 2017. His research is in the areas of mathematical statistics and information theory.
